Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-28 manuscript/manuscript.tex
Fix typos

\title[Variable Density Tesseroids]{
    Gravitational field calculation in spherical coordinates using variable
    densities in depth
}
\author[S.R. Soler, A. Pesce, L. Uieda and M.E. Gimenez]{
    Santiago R. Soler$^{1,2}$, Agustina Pesce$^{1,2}$, Leonardo Uieda$^3$ and
    Mario E. Gimenez$^{1,2}$ \\
    $^1$CONICET, Argentina.~e-mail: santiago.r.soler@gmail.com\\
    $^2$Instituto Geofísico Sismológico Volponi, Universidad Nacional de
    San Juan, Argentina\\
    $^3$Department of Earth Sciences, SOEST, University of Hawai‘i at
    M\={a}noa, Honolulu, Hawaii, USA
}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{
    Gravitational effects of the Nequ\'en sedimentary basin modelled
    using tesseroids with an exponential density function of depth.
    (a)~Topography of the Neuqu\'en Basin (in km) and its location in South America,
    (b)~thickness of the sedimentary basin \citep[in meters;][]{Heine2007},
    (c)~resulting gravitational potential $V$,
    (d)~resulting vertical component of the gradient ($g_z$),
    calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by the tesseroid model of the
    Neuqu\'en basin with an exponential density contrast and with a homogenenous and
    linear density variation.
    \mbox{(a)-(b)}~Differences on $V$ and $g_z$ between the exponential density model
    and the homogenenous density one,
    \mbox{(c)-(f)}~differences on $V$ and $g_z$ between the exponential density model
    and the linear density one, calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin-diffs}
\end{figure*}

>>>>

\title[Variable Density Tesseroids]{
    Gravitational field calculation in spherical coordinates using variable
    densities in depth
}
\author[S.R. Soler, A. Pesce, L. Uieda and M.E. Gimenez]{
    Santiago R. Soler$^{1,2}$, Agustina Pesce$^{1,2}$, Leonardo Uieda$^3$ and
    Mario E. Gim\'enez$^{1,2}$ \\
    $^1$CONICET, Argentina.~e-mail: santiago.r.soler@gmail.com\\
    $^2$Instituto Geofísico Sismológico Volponi, Universidad Nacional de
    San Juan, Argentina\\
    $^3$Department of Earth Sciences, SOEST, University of Hawai‘i at
    M\={a}noa, Honolulu, Hawaii, USA
}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{
    Gravitational effects of the Neuqu\'en sedimentary basin modelled
    using tesseroids with an exponential density function of depth.
    (a)~Topography of the Neuqu\'en Basin (in km) and its location in South America,
    (b)~thickness of the sedimentary basin \citep[in meters;][]{Heine2007},
    (c)~resulting gravitational potential $V$,
    (d)~resulting vertical component of the gradient ($g_z$),
    calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by the tesseroid model of the
    Neuqu\'en basin with an exponential density contrast and with a homogeneous and
    linear density variation.
    \mbox{(a)-(b)}~Differences on $V$ and $g_z$ between the exponential density model
    and the homogeneous density one,
    \mbox{(c)-(f)}~differences on $V$ and $g_z$ between the exponential density model
    and the linear density one, calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin-diffs}
\end{figure*}
